A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-22 text/conclusion.tex
Rewrite conclusion.

We have proposed a new multi-stage calculus \LMD with dependent types.
\LMD enables finer-grained typing of multi-stage programming comparing to existing type systems.
This extension prevents some bugs relating to generated functions with multi-stage programming,
such as \verb|vadd| function for vectors of a fixed length.
We proved properties of \LMD including preservation, confluence, 
strong normalization for full reduction, and progress for staged reduction.
The technical difficulty of extension is how to deal with the symbol of CSP $\%$ in the equation rules.
We resolve this problem by ignoring $\%$ under some condition.

Developing a typechecking algorithmic for \LMD is left for future work.
They would be complicated but possible 
because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.

>>>>

We have proposed a new multi-stage calculus \LMD with dependent types,
which make it possible for programmers to express finer-grained
properties about the behavior of code values.  The combination leads
to augmentation of almost all judgments in the type system with stage
information.  CSP and type equivalence specially tailored for it are
keys to expressing dependently typed practical code generators.  We
have proved basic properties of \LMD, including preservation,
confluence, strong normalization for full reduction, and progress for
staged reduction.

Developing a typechecking algorithmic for \LMD is left for future
work.  We expect that most of the development is straigtforward,
except for implicit CSP at the type-level and \%-erasing equivalence
rules.
